### 2019-12-26 README.Rmd
make readme a lil cozier, update examples!

# infer R Package <img src="https://github.com/tidymodels/infer/blob/develop/figs/infer_gnome.png?raw=true" align="right" width=125 />

@@

The objective of this package is to perform statistical inference using an expressive statistical grammar that coheres with the `tidyverse` design framework.

```{r diagram, echo=FALSE}
knitr::opts_chunk$set(eval = FALSE)
knitr::include_graphics("https://raw.githubusercontent.com/tidymodels/infer/master/figs/ht-diagram.png")
```

@@

```{r}
install.packages("infer")
```

To install the developmental version of `infer`, make sure to install `remotes` first. The `pkgdown` website for this developmental version is at <https://infer.netlify.com>.

```{r}
install.packages("remotes")
remotes::install_github("tidymodels/infer")
```

@@

```{r}
install.packages("remotes")
remotes::install_github("tidymodels/infer", ref = "develop")
```

To see the things we are working on with the package as vignettes/Articles, check out 
the developmental `pkgdown` site at <https://infer-dev.netlify.com>.

@@

We welcome others helping us make this package as user friendly and efficient as possible. Please review
our [contributing](https://github.com/tidymodels/infer/blob/develop/CONDUCT.md) and [conduct](CONDUCT.md) guidelines. Of particular interest is
helping us to write `testthat` tests and in building vignettes that show how to (and how NOT to)
use the package. By participating in this project you agree to abide by its terms.

@@

These examples assume that `mtcars` has been overwritten so that the variables `cyl`, `vs`, `am`, `gear`, and `carb` are `factor`s.

```{r}
mtcars <- as.data.frame(mtcars) %>%
  mutate(cyl = factor(cyl),
          vs = factor(vs),
          am = factor(am),
          gear = factor(gear),
          carb = factor(carb))
```

Hypothesis test for a difference in proportions (using the formula interface 
`y ~ x` in `specify()`):

```{r}
mtcars %>%
  specify(am ~ vs, success = "1") %>%
  hypothesize(null = "independence") %>%
  generate(reps = 100, type = "permute") %>%
  calculate(stat = "diff in props", order = c("1", "0"))
```

Confidence interval for a difference in means (using the non-formula interface
giving both the `response` and `explanatory` variables in `specify()`):

```{r}
mtcars %>%
  specify(response = mpg, explanatory = am) %>%
  generate(reps = 100, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("1", "0"))
```

Note that the formula and non-formula interfaces work for all implemented inference
procedures in `infer`. Use whatever is more natural for you. If you will be doing
modeling using functions like `lm()` and `glm()`, we recommend you begin to use the
formula `y ~ x` notation as soon as possible though.

Other examples are available in the package vignettes.

>>>>

# infer R Package <img src="https://github.com/tidymodels/infer/blob/master/figs/infer_gnome.png?raw=true" align="right" width=125 />

@@

The objective of this package is to perform statistical inference using an expressive statistical grammar that coheres with the `tidyverse` design framework. The package is centered around 4 main verbs, supplemented with many utilities to visualize and extract value from their outputs.

+ `specify()` allows you to specify the variable, or relationship between variables, that you're interested in.
+ `hypothesize()` allows you to declare the null hypothesis.
+ `generate()` allows you to generate data reflecting the null hypothesis.
+ `calculate()` allows you to calculate a distribution of statistics from the generated data to form the null distribution.

To learn more about the principles underlying the package design, see `vignette("infer")`.

```{r load-package, echo = FALSE, message = FALSE, warning = FALSE}
library(devtools)
devtools::load_all()
```

```{r diagram, echo=FALSE}
knitr::include_graphics("https://raw.githubusercontent.com/tidymodels/infer/master/figs/ht-diagram.png")
```

@@

```{r, eval = FALSE}
install.packages("infer")
```

To install the developmental version of `infer`, make sure to install `remotes` first. The `pkgdown` website for this version is at <https://infer.netlify.com>.

```{r, eval = FALSE}
install.packages("remotes")
remotes::install_github("tidymodels/infer")
```

@@

```{r, eval = FALSE}
install.packages("remotes")
remotes::install_github("tidymodels/infer", ref = "develop")
```

To see documentation for the developmental version of `infer`, the developmental `pkgdown` site is available at <https://infer-dev.netlify.com>.

@@

We welcome others helping us make this package as user-friendly and efficient as possible. Please review
our [contributing](https://github.com/tidymodels/infer/blob/master/CONTRIBUTING.md) and [conduct](https://github.com/tidymodels/infer/blob/master/CONDUCT.md) guidelines. Please see the open [issues](https://github.com/tidymodels/infer/issues) for more specific fixes/additions needing attention. By participating in this project you agree to abide by its terms.

@@

These examples are pulled from the "Full infer Pipeline Examples" vignette, accessible by calling `vignette("observed_stat_examples")`. They make use of the `gss` dataset supplied by the package, providing a sample of data from the [General Social Survey](https://gss.norc.org). The data looks like this:

```{r load-gss, warning = FALSE, message = FALSE}
# load in the dataset
data(gss)

# take a glimpse at it
str(gss)
```

As an example, we'll run an analysis of variance on `age` and `partyid`, testing whether the age of a respondent is independent of their political party affiliation.

Calculating the observed statistic,

```{r, message = FALSE, warning = FALSE}
F_hat <- gss %>% 
  specify(age ~ partyid) %>%
  calculate(stat = "F")
```

Then, generating the null distribution,

```{r, message = FALSE, warning = FALSE}
null_distn <- gss %>%
   specify(age ~ partyid) %>%
   hypothesize(null = "independence") %>%
   generate(reps = 1000, type = "permute") %>%
   calculate(stat = "F")
```

Visualizing the observed statistic alongside the null distribution,

```{r, message = FALSE, warning = FALSE}
visualize(null_distn) +
  shade_p_value(obs_stat = F_hat, direction = "greater")
```

Calculating the p-value from the null distribution and observed statistic,

```{r, message = FALSE, warning = FALSE}
null_distn %>%
  get_p_value(obs_stat = F_hat, direction = "greater")
```

Note that the formula and non-formula interfaces  (i.e. `age ~ partyid` vs. `response = age, explanatory =  partyid`) work for all implemented inference procedures in `infer`. Use whatever is more natural for you. If you will be doing modeling using functions like `lm()` and `glm()`, though, we recommend you begin to use the formula `y ~ x` notation as soon as possible.

Other resources are available in the package vignettes! See `vignette("observed_stat_examples")` for more examples like the one above, and `vignette("infer")` for discussion of the underlying principles of the package design.
